A generic and fast C++ optimization framework

### 2017-10-21 paper.tex
Fix clamps and update optimizer output.

  double Evaluate(const arma::mat& para, size_t s, size_t bs) {
    double cost = 0;
    for (size_t i = s; i < s + bs; i++)
      cost += (para(ord[i]) * para(ord[i]) + bi(ord[i]) * para[i] + in(ord[i]);
    return cost;
  }

@@

  template<typename FunctionType>
  double Optimize(FunctionType& function, arma::mat& parameter) {
    arma::mat gradient;
    for (size_t i = 0; i < 5000; i += bs) {
      if ((i % function.NumFunctions() == 0) { function.Shuffle(); }
      function.Gradient(parameter, i % function.NumFunctions(), gradient, bs);
      parameter -= lr * gradient;
    }
    return function.Evaluate(parameter, 0, function.NumFunctions());
  }
  size_t bs; double lr; // Store batch size and learning rate internally.
};
\end{minted}
\vspace{-0.3em}
%\caption{Simple stochastic gradient descent method with a static number of
%iterations to optimize the function parameter ({\tt bs} defines the batch size
%and {\tt lr} the learning rate). )}
%\vspace{-0.6em}
%\end{listing}
%\vspace{-0.8em}

@@

When we run this code, we receive the output: {\tt objective: 123.8 }

>>>>

  double Evaluate(const arma::mat& para, size_t s, size_t bs) {
    double cost = 0;
    for (size_t i = s; i < s + bs; i++)
      cost += para(ord[i]) * para(ord[i]) + bi(ord[i]) * para(ord[i]) + in(ord[i]);
    return cost;
  }

@@

  template<typename FunctionType>
  double Optimize(FunctionType& function, arma::mat& parameter) {
    arma::mat gradient;
    for (size_t i = 0; i < 5000; i += bs) {
      if (i % function.NumFunctions() == 0) { function.Shuffle(); }
      function.Gradient(parameter, i % function.NumFunctions(), gradient, bs);
      parameter -= lr * gradient;
    }
    return function.Evaluate(parameter, 0, function.NumFunctions());
  }
  size_t bs; double lr; // Store batch size and learning rate internally.
};
\end{minted}
\vspace{-0.3em}
%\caption{Simple stochastic gradient descent method with a static number of
%iterations to optimize the function parameter ({\tt bs} defines the batch size
%and {\tt lr} the learning rate). )}
%\vspace{-0.6em}
%\end{listing}
%\vspace{-0.8em}

@@

When we run this code, we receive the output: {\tt objective: 123.75 }
